---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
library(forcats)
```

```{css}

```

## Observing how I work on my assignments




```{r}
survey_data <- read_csv('https://docs.google.com/spreadsheets/d/e/2PACX-1vQUixhbLRVb7xeTMmBd6zgRqk-xy9kFFPYV14-xRnR-Lt_pwez9hfV8rMe8uPgvZb071VBBXp4rujYX/pub?gid=1995340242&single=true&output=csv')

```



```{r}

# Renaming the variables

survey_data_renamed <- survey_data %>%
  rename(date = 1,
         subject = 2,
         time = 3,
         minutes = 4
         )

#Making a group
subject_group <- survey_data_renamed |> 
  group_by(subject) |> 
  summarise(
    total_minutes_subject = sum(minutes)
  ) 



```




```{r}
# Number of sessions by subject

survey_data_renamed %>% 
ggplot() +
  geom_bar(aes(x = fct_infreq(subject))) +
  scale_y_continuous(breaks = seq(0, 10, by =1)) +
  labs(x = "Subject")

# Number of Sessions by time of day

survey_data_renamed %>%
  ggplot(aes(x = fct_relevel(time, "Morning ( 7am - 12pm)"))) +
  geom_bar() +
  scale_y_continuous(breaks = seq(0, 10, by = 1)) +
  labs(x = "Time of Day")

#total time per subject in minutes
subject_group |> 
  ggplot(aes(x = subject, y = total_minutes_subject, fill = subject)) + 
  geom_col() +
  labs(
    title = "Total minutes spent on assignments by subject",
    x = "Subject",
    y = "Minutes",
  )
```


### Summary values and proportions

```{r}
# average assignment session
survey_data_renamed$minutes |>  mean()


# range
survey_data_renamed$minutes |>  range()




#proportion of time spent working on assignments for each subject

#Phil 327
subject_group$total_minutes_subject[1] / (subject_group$total_minutes_subject |>  sum())

#Phil 360
subject_group$total_minutes_subject[2] / (subject_group$total_minutes_subject |>  sum())

#Stats 220
subject_group$total_minutes_subject[3] / (subject_group$total_minutes_subject |>  sum())

#Stats 330
subject_group$total_minutes_subject[4] / (subject_group$total_minutes_subject |>  sum())
```


### Dynamic comments

Regarding individual assignment study sessions,
the average length of a session was `r mean(survey_data_renamed$minutes)` minutes and the range was `r range(survey_data_renamed$minutes)`

Regarding time spent on assignments by subject,
I spent `r subject_group$total_minutes_subject[1] / (subject_group$total_minutes_subject |>  sum()) ` of my time on Phil 327, `r subject_group$total_minutes_subject[2] / (subject_group$total_minutes_subject |>  sum()) ` of my time on Phil 360, `r subject_group$total_minutes_subject[3] / (subject_group$total_minutes_subject |>  sum()) ` of my time on Stats 220 and `r subject_group$total_minutes_subject[4] / (subject_group$total_minutes_subject |>  sum()) ` of my time on Stats 330
